---
title: "Amplifying low-light images"
author: "Olivia Brode-Roger"
date: "7/25/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(reshape2)
library(jpeg)
```

We took very low-light images of clouds at night from a cellphone, this is an
attempt to recover *something* from those images.

Really all that's happening is a plotting of the raw values scaled to a color
scale that's not just black, black, and slightly less black... Turns out, still
can't see anything :(


The "1", "2", and "3" correspond to the red, green, and blue channels. I 
would've fixed this had it worked, but I think this is the end of this work...

```{r read-img, }
for (filename in list.files(pattern = "*.jpg")) {
    img <- filename %>%
        readJPEG() %>% 
        melt() %>% 
        as_tibble() %>% 
        rename(x = Var1,
               y = Var2,
               col = Var3)
    
    p <- img %>% 
        ggplot(aes(x = x,
                   y = y,
                   fill = value)) +
        geom_raster() +
        facet_wrap(~ col)
        
    print(p)
}
```
